% Appendix B

\chapter{Sensor Board Choice} % Main appendix title

\label{AppendixB} % For referencing this appendix elsewhere, use \ref{AppendixA}

%\lhead{Appendix B. \emph{Sensor Board Choice}} % This is for the header on each page - perhaps a shortened title

This document was part of one of the BuB4EU workshops we attended, as mentioned in Chapter \ref{Chapter4}. More precisely, this workshop helped me chose Arduino over other platforms.

Initially we had lots of Crossbow TelosB rev. B nodes\footnote{\url{http://bullseye.xbow.com:81/Products/productdetails.aspx?sid=252}} ready to use in the laboratory so this was quite a good option to consider. They run over an embedded Unix-based operating system ---TinyOS---, which brings several advantages such as default multithreading, advanced customization options, etc. However this board lacks the community and good documentation that other platforms such Arduino and its derivatives do have. Also, complexity when using this platform is high.  

Hence contemplating another options such as the one mentioned before is a must. Arduino, while maintaining simplicity, is as well a very powerful platform used by many hackers and hobbyists today. This, along with its open source philosophy has created a large community that has been very active for the past years. Moreover, many companies create modules for this prototyping platform to extend its original functionalities. It does support ZigBee ---which is a prerequisite--- through an external module called XBee.

Therefore, being complexity my main criteria I chose Arduino as my sensing board to complete this project.
